Computable Compressed Matrices\\Suplementary Material

### 2014-01-27 manuscript.tex
atualizacao referencias figuras

The results are represented in Figures \ref{fig39}, \ref{fig40} and \ref{fig41} for the PUA Method and in Figures 26, 27 and 28 for the 
BFM Methods.  A computer with 8 GB of RAM Memory, 16 GB of swap, processor core i7 model 870\todo{confirmar modelo}
and operational 
system Linux Debian 7.0 was used to perform this simulation. In Figure \ref{fig39}, it is possible to verify the approximate 
moment  when the  the storage in disk (swaap) begins to be used. This is indicated by the vertical green line. 
At this moment, the bitstring method becomes faster than the traditional method because it does not require disk 
storage due tocompressed memory representation. Note that, in the Figure \ref{fig40}, the traditional method is faster 
than the bitstring one before the beginning of the disk access. However, after it becomes necessary use the disk 
so that the matrix can be accessed and stored, , the traditional method  becames slower (Figura \ref{fig41}). 
These results 
indicate that the bistring method can promote the optimization of the memory use because the access to the main 
memories (RAM and cache) are faster than the access to secondary memories (disk). In Figures \ref{fig42}, 
\ref{fig43} and \ref{fig44} the 
results of the processing time for  the BFM method are represented. Once again, a vertical green line indicates 
the approximate moment when the disk access begins. There is a difference in relation to the PUA method since the 
BMF method uses the PUA values to perform its calculation. Therefore, the BMF method demands more memory to be 
processed, which reduces the matrix dimensions involved in the process, represented in the main memory. As 
indicated in Figure \ref{fig41}, for the PUA method, and Figure \ref{fig44}, for the BMF method, it is possible 
to verify that 
before the access to the disk, the traditional method is faster than the bitstring one, but once the access 
is initiated,  the bitstring method becames faster.

@@

% Do NOT remove this, even if you are not including acknowledgments
\section*{Acknowledgments}
We would like to thank Claudia Torres Code\c{c}o, Moacyr Silva and Paulo
Cezar Carvalho for fruitful discussions and key ideas which helped improve the
manuscript.

>>>>

The results are represented in Figures \ref{fig39}, \ref{fig40} and \ref{fig41} for the PUA Method and in Figures 
\ref{fig42}, \ref{fig43} and \ref{fig44} for the 
BFM Methods.  A computer with 8 GB of RAM Memory, 16 GB of swap, processor core i7 model 870  \todo{confirmar modelo}
and operational 
system Linux Debian 7.0 was used to perform this simulation. In Figure \ref{fig39}, it is possible to verify the approximate 
moment  when the  the storage in disk (swaap) begins to be used. This is indicated by the vertical green line. 
At this moment, the bitstring method becomes faster than the traditional method because it does not require disk 
storage due tocompressed memory representation. Note that, in the Figure \ref{fig40}, the traditional method is faster 
than the bitstring one before the beginning of the disk access. However, after it becomes necessary use the disk 
so that the matrix can be accessed and stored, , the traditional method  becames slower (Figura \ref{fig41}). 
These results 
indicate that the bistring method can promote the optimization of the memory use because the access to the main 
memories (RAM and cache) are faster than the access to secondary memories (disk). In Figures \ref{fig42}, 
\ref{fig43} and \ref{fig44} the 
results of the processing time for  the BFM method are represented. Once again, a vertical green line indicates 
the approximate moment when the disk access begins. There is a difference in relation to the PUA method since the 
BMF method uses the PUA values to perform its calculation. Therefore, the BMF method demands more memory to be 
processed, which reduces the matrix dimensions involved in the process, represented in the main memory. As 
indicated in Figure \ref{fig41}, for the PUA method, and Figure \ref{fig44}, for the BMF method, it is possible 
to verify that 
before the access to the disk, the traditional method is faster than the bitstring one, but once the access 
is initiated,  the bitstring method becames faster.

@@

% Do NOT remove this, even if you are not including acknowledgments
\section*{Acknowledgments}
We would like to thank Claudia Torres Code\c{c}o, Moacyr Silva and Paulo
Cezar Carvalho for fruitful discussions and key ideas which helped improve the
manuscript.\todo{Adicionar a Carol}
